\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-30 paper.qmd
Updated acknowledgement

```{r}
#| label: load-libraries
#| warning: false
#| echo: false
# remotes::install_github("JayaniLakshika/quollr")
library(quollr)
library(tibble)
library(dplyr)
# remotes::install_github("jlmelville/snedata")
# library(snedata)
# library(ggflowchart)
#library(purrr) ## map function
#library(gridExtra) ## for grid.arrange
# library(rsample)
# library(DT)
library(ggbeeswarm)
library(ggplot2)
library(readr)
library(tidyr)

library(Rtsne)
library(uwot)
library(phateR)
library(patchwork)
library(png)
library(langevitour)
library(colorspace)
library(kableExtra)
library(grid)
library(conflicted)
conflicts_prefer(dplyr::filter)
```

@@

These `R` packages were used for the work:
The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.

>>>>

```{r}
#| label: load-libraries
#| warning: false
#| echo: false
# remotes::install_github("JayaniLakshika/quollr")
library(quollr)
library(tibble)
library(dplyr)
# remotes::install_github("jlmelville/snedata")
# library(snedata)
# library(ggflowchart)
#library(purrr) ## map function
#library(gridExtra) ## for grid.arrange
# library(rsample)
# library(DT)
#library(ggbeeswarm)
library(ggplot2)
library(readr)
library(tidyr)

# library(Rtsne)
# library(uwot)
# library(phateR)
library(patchwork)
library(png)
#library(langevitour)
library(colorspace)
library(kableExtra)
#library(grid)
library(conflicted)
conflicts_prefer(dplyr::filter)
```

@@

These `R` packages were used for the work:. These `python` packages were used for the work:. The article was created with `R` packages `rticles`, `knitr`, and `rmarkdown`. The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.

### 2024-09-30 paper.tex
Updated acknowledgement

These \texttt{R} packages were used for the work: The project's GitHub
repository
(\url{https://github.com/JayaniLakshika/paper-nldr-vis-algorithm})
contains all materials required to reproduce this article.

>>>>

These \texttt{R} packages were used for the work:. These \texttt{python}
packages were used for the work:. The article was created with
\texttt{R} packages \texttt{rticles}, \texttt{knitr}, and
\texttt{rmarkdown}. The project's GitHub repository
(\url{https://github.com/JayaniLakshika/paper-nldr-vis-algorithm})
contains all materials required to reproduce this article.
